Updates on the Exoplanet Orbit Database

### 2014-02-25 draft/ms.tex
Updates on sec 2.4

\textit{Sharon: I don't think the first sentence is true... Looking at
  the fields in the Planet Information section in the table, it
  doesn't contain when who or how at all... The current way of
  dividing fields into these categories is a bit weird, but we are
  definitely not changing it in our paper or change the website any
  time soon... I'm guessing you want to summarize what Planet
  Information fields cover in the first sentence here, so maybe look
  at the table and give a very general summary of what those fields
  are.
  I'm not sure what's the purpose of the second sentence... It sounds
  like something we generally did for EOD. Maybe we should move it to
  the paragraph above in the overview text for
  Section~\ref{sec:update}. Think more about what the purpose of the
  subsection overview should serve.}

@@

LAMBDA: We report the projected spin-orbit misalignment of transiting systems. We follow the definition of Fabrycky and Winn 2009. The spin-orbit angle is defined to be the angle between the stellar spin axis and the orbital axis. However, since the spin-orbit angle is not directly measurable, and therefore lambda, the projected spin-orbit angle was introduced. In the observer-oriented frame, Z axis points toward the observer, X axis points along the intersection of the sky plane and the planet's orbital plane, and Y axis completes a right handed-triad. Lambda is measured clockwise on the sky from the Y axis to the projected stellar rotational axis. While maintaining LAMBDA in our database, we figured out that literatures have conflicted definitions of LAMBDA with $\beta$, which is equal to $\lambda$ = -$\beta$. We sorted these cases out and made sure that LABDA is following the definition of Fabrycky and Winn 2009.

I: it used to be for transit systems only. Now sometimes for
non-transiting systems the values of I are also available.
ZZZ I was not added I think... and if the system has a follow-up transit observation?

@@

RR

%------------------------------------------------------------------------------
\subsection{Secondary Eclipse}

@@

SE

SEDEPTH J H KS KP 36 45 58 80

SET

@@

We provide the brightness of the host star measured in different wavelengths. We report optical magnitudes (V and B-V), 2MASS J,H, and K magnitudes centered at 1.2\micron, 1.7\micron, and 2.2\micron, respectively.

>>>>

@@

LAMBDA is the projected spin-orbit misalignment in the unit of degree. We report the projected spin-orbit misalignment of transiting systems. We follow the definition of Fabrycky and Winn 2009. The spin-orbit angle is defined to be the angle between the stellar spin axis and the orbital axis. However, since the spin-orbit angle is not directly measurable, and therefore lambda, the projected spin-orbit angle was introduced. In the observer-oriented frame, Z axis points toward the observer, X axis points along the intersection of the sky plane and the planet's orbital plane, and Y axis completes a right handed-triad. Lambda is measured clockwise on the sky from the Y axis to the projected stellar rotational axis. While maintaining LAMBDA in our database, we figured out that literatures have conflicted definitions of LAMBDA with $\beta$, which is equal to $\lambda$ = -$\beta$. We sorted these cases out and made sure that LABDA is following the definition of Fabrycky and Winn 2009.

I is the orbital inclination. This field is not newly added but we chose to describe it here since our database now has the inclination for planets detected by methods other than transit. Previously, only transiting systems used to have the inclination measured. However, now sometimes for
non-transiting systems the values of I are also available. For instance, if the system was first detected by radial velocity and has a follow-up transit observation, then the inclination can be measured. To sum up, all the transiting planets have measured orbital inclination and currently, we also have one microlensing planet with measured inclination. *** give the example!

you can only measure inclination with transit and imaging but there is only one microlensing planet with the inclination

@@

RR is the ratio of the planetary radius and the stellar radius. Previously, we only reported the transit depth, which is the square of the planetary radius and the stellar radius.
=== Why did we add this field?

%------------------------------------------------------------------------------
\subsection{Secondary Eclipse}
We have added an entire new set of fields for the secondary eclipse. Since \cite{Wright2011},

@@

SE flag indicates whether the system has detected secondary eclipse in any of the 2MASS J, H, and K$_s$, Kepler photometry band, and 4 Spitzer IRAC bands. SE is a boolean and being true indicates the system has detected secondary eclipse.

SEDEPTH J H KS KP 36 45 58 80 fields are the secondary eclipse depth measured in the corresponding wavelength band. J, K, and K$_s$ are the depth measured in the 2MASS wavelength band in near infrared each centered at 1.25\micron, 1.65\micron, and 2.15\micron, respectively. KP is the depth measured in the Kepler photometry band which is centered at

SET is the epoch of secondary eclipse center in HJD.

@@

We provide the brightness of the host star measured in different wavelengths. We report optical magnitudes (V and B-V), 2MASS J,H, and K magnitudes centered at 1.25\micron, 1.65\micron, and 2.15\micron, respectively.
